---
title: "Hangman Documentation"
author: "Karl-Heinz Reisenauer"
date: "31 Januar 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Overview

This document describes how to run this application and how to use it.

This application has been inspired by Marek Hlavac (Political Economy and Government, Harvard University). 

He has written a Hangman game in R and I wanted to convert it into a Shiny app.
I have taken over the words to be guessed and some code fragmente and added the "HD" graphics and the Shniny part :).

The original can be found here:
https://sites.google.com/site/marekhlavac/computer-games-written-in-r

## Dependencies

The following libraries are required, please install, if not present:

- shiny
- plotrix
- htmlTable

Install with:

```{r , eval=FALSE}
install.packages("shiny")
install.packages("plotrix")
install.packages("htmlTable")
```

## Run and Usage

### Run
To start the application, make sure that these three files are in the same directory:

- ui.R
- server.R
- hangman.rdata

Switch to the application directory:
```{r, eval=FALSE}
    setwd("path/to/Hangman")
```

Run the Application

```{r, eval=FALSE}
    runApp('Hangman')
```

### Useage

In this application you have to guess a random word. 
You have to type letters in the text field. If you gess right , the letter appears in the word, if you guess wrong ... u will see.
After the seventh wrong guess, you have lost.
Either way, you can always start a new game by pressing the "new Game" button.